### 2008-09-02 doc/storage_system/arc1-storage-documentation.tex
hopi -> Hopi (uppercase)

The Shepherd could communicate with the file transfer services via backend modules. Currently there are two kinds of backend modules, one for the \emph{byteio} service (which is a simple implementation of a subset of the ByteIO interface) and one for the \emph{hopi} service (which is a simple HED-based HTTP server).

@@

Let's see the scenario for the hopi service which should be in a special `slave' mode for this kind of operation: if a client asks for a file called \verb!file1!, and this file is in the store directory (\verb!./store/file!), then the Shepherd service creates a hardlink into the transfer directory (e.g.~\verb!./transfer/abc!) and sets this file read-only. If the hopi service is configured that way that it handles the HTTP path \verb!/prb! and it is serving files from the directory \verb!./transfer! then after the hardlink is created, we have this URL for this file: \verb!http://localhost:60000/prb/abc!. Now we can give this URL to the client. Then the client \verb!GET!s this URL and gets the file. The hopi service removes (unlinks) this file immediately after the \verb!GET! request arrived, which makes this \verb!http://localhost:60000/prb/abc! URL invalid (so this is a one-time URL), but because of the hardlink the file is still there in the store directory, it is just removed from the transfer directory. Now if some other user wants this file, the Shepherd creates an other hardlink, e.g.~\verb!./transfer/qwe! and now we have an URL \verb!http://localhost:60000/prb/qwe!.

If a client wants to upload a new file, then the Shepherd creates an empty file in the store directory, e.g.~\verb!./store/file2! and creates a hardlink into the transfer directory, e.g.~\verb!./transfer/oiu! and makes it writable, and now we have a URL \verb!http://localhost:60000/prb/oiu!, and the client is able to do a \verb!PUT! to this URL. When the client \verb!PUT!s the file there, the hopi service immediately removes the uploaded file from the transfer directory, but because it has a hardlink in the store directory, the file is stored there as \verb!./store/file2!. The backend module for the hopi service periodically checks whether a new file has two or just one hard links. If it has only one that means that a file is uploaded, so it could notify the Shepherd that the file is arrived. In order to do that, all the backend modules get a callback method `file\_arrived' from the Shepherd.

>>>>

The Shepherd could communicate with the file transfer services via backend modules. Currently there are two kinds of backend modules, one for the \emph{byteio} service (which is a simple implementation of a subset of the ByteIO interface) and one for the \emph{Hopi} service (which is a simple HED-based HTTP server).

@@

Let's see the scenario for the Hopi service which should be in a special `slave' mode for this kind of operation: if a client asks for a file called \verb!file1!, and this file is in the store directory (\verb!./store/file!), then the Shepherd service creates a hardlink into the transfer directory (e.g.~\verb!./transfer/abc!) and sets this file read-only. If the Hopi service is configured that way that it handles the HTTP path \verb!/prb! and it is serving files from the directory \verb!./transfer! then after the hardlink is created, we have this URL for this file: \verb!http://localhost:60000/prb/abc!. Now we can give this URL to the client. Then the client \verb!GET!s this URL and gets the file. The Hopi service removes (unlinks) this file immediately after the \verb!GET! request arrived, which makes this \verb!http://localhost:60000/prb/abc! URL invalid (so this is a one-time URL), but because of the hardlink the file is still there in the store directory, it is just removed from the transfer directory. Now if some other user wants this file, the Shepherd creates an other hardlink, e.g.~\verb!./transfer/qwe! and now we have an URL \verb!http://localhost:60000/prb/qwe!.

If a client wants to upload a new file, then the Shepherd creates an empty file in the store directory, e.g.~\verb!./store/file2! and creates a hardlink into the transfer directory, e.g.~\verb!./transfer/oiu! and makes it writable, and now we have a URL \verb!http://localhost:60000/prb/oiu!, and the client is able to do a \verb!PUT! to this URL. When the client \verb!PUT!s the file there, the Hopi service immediately removes the uploaded file from the transfer directory, but because it has a hardlink in the store directory, the file is stored there as \verb!./store/file2!. The backend module for the Hopi service periodically checks whether a new file has two or just one hard links. If it has only one that means that a file is uploaded, so it could notify the Shepherd that the file is arrived. In order to do that, all the backend modules get a callback method `file\_arrived' from the Shepherd.
